Counting And Confusion: Bayesian Rate Estimation With Multiple Populations

### 2013-02-20 many.tex
Fixed spelling typo.

Two alternative approaches to rate estimation have been suggested and
are commonly used.  One, known as the \emph{loudest-event statistic}
\cite{Biswas2009,Brady2004,Brady2008}, uses only the information from
the highest-ranked event in the data to infer the rate distribution.
This approach has been used successfully
\cite{s5-lowmass,s5-lowmass-2,s5-highmass,s5-highmass-erratum,s6-lowmass,s6-highmass}
when the number of loud foreground events is small (typically zero or
one) to obtain upper limits on foreground rates.  However, the
loudest-event statistic ignores all events except the loudest one, and
so suffers from an unnecessary loss of information; therefore, we
expect it to yield a much larger variance than strictly necessary when
multiple events are present in the data.  In practice, the
loudest-event statistic is typically applied repeatedly to multiple
``chunks'' of data, using the estimated rate posterior from each chunk
as a rate prior for the next chunk's analysis
\cite{s5-lowmass-2,s5-highmass,s5-highmass-erratum}.  Even when used
in this mode, the method discards information, with the amout of
information loss depending on the (arbitrary) division of the data
into chunks.

>>>>

Two alternative approaches to rate estimation have been suggested and
are commonly used.  One, known as the \emph{loudest-event statistic}
\cite{Biswas2009,Brady2004,Brady2008}, uses only the information from
the highest-ranked event in the data to infer the rate distribution.
This approach has been used successfully
\cite{s5-lowmass,s5-lowmass-2,s5-highmass,s5-highmass-erratum,s6-lowmass,s6-highmass}
when the number of loud foreground events is small (typically zero or
one) to obtain upper limits on foreground rates.  However, the
loudest-event statistic ignores all events except the loudest one, and
so suffers from an unnecessary loss of information; therefore, we
expect it to yield a much larger variance than strictly necessary when
multiple events are present in the data.  In practice, the
loudest-event statistic is typically applied repeatedly to multiple
``chunks'' of data, using the estimated rate posterior from each chunk
as a rate prior for the next chunk's analysis
\cite{s5-lowmass-2,s5-highmass,s5-highmass-erratum}.  Even when used
in this mode, the method discards information, with the amount of
information loss depending on the (arbitrary) division of the data
into chunks.
